Assessing Virulence by MCG

### 2017-09-06 doc/RMD/MCG-virulence.Rmd
update graph to use a better binwidth

plot.median <- function(x) {
  m <- mean(x, na.rm = TRUE)
  c(y = m, ymin = m, ymax = m)
}

ggplot(region_dat, aes(x = Region, y = Severity)) +
  ggforce::geom_sina(aes(fill = Source), 
             pch = 21, 
             alpha = 0.4) +
  # geom_point(aes(fill = Source), 
  #            pch = 21, 
  #            position = position_jitter(width = 0.25), 
  #            alpha = 0.35) +
  # geom_boxplot(alpha = 0.5) +
  stat_summary(fun.data = "plot.median", geom = "errorbar", colour = "black", width = 0.6, size = 2, alpha = 0.5) +
  stat_summary(fun.data = "plot.median", geom = "errorbar", colour = "white", width = 0.5, size = 1, alpha = 1) +
  scale_y_continuous(limits = c(1, 9), breaks = c(1, 3, 5, 7, 9), expand = c(0, 0.1)) +
  scale_fill_manual(values = rev(c("black", "white"))) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/2) +
  theme(axis.text = element_text(color = "black")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(colour = "grey50")) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(legend.position = "top") +
  theme(plot.margin = unit(c(0, 0, 0, 0), "lines")) +
  labs(list(
    y = "Aggressiveness",
    x = "Region"
    ))
if (!interactive()){
  ggsave(file.path("results", "figures", "publication", "aggressiveness.pdf"),
         width = 88, units = "mm")
}
```

>>>>

plot.mean <- function(x) {
  m <- mean(x, na.rm = TRUE)
  c(y = m, ymin = m, ymax = m)
}

set.seed(2017-09-06)
ggplot(region_dat, aes(x = Region, y = Severity)) +
  ggforce::geom_sina(aes(fill = Source), 
                     pch = 21, 
                     binwidth = 0.1, 
                     alpha = 0.4) +
  # geom_point(aes(fill = Source), 
  #            pch = 21, 
  #            position = position_jitter(width = 0.25), 
  #            alpha = 0.35) +
  # geom_boxplot(alpha = 0.5) +
  stat_summary(fun.data = plot.mean, geom = "errorbar", colour = "black", width = 0.6, size = 2, alpha = 0.5) +
  stat_summary(fun.data = plot.mean, geom = "errorbar", colour = "white", width = 0.5, size = 1, alpha = 1) +
  scale_y_continuous(limits = c(1, 9), breaks = c(1, 3, 5, 7, 9), expand = c(0, 0.1)) +
  scale_fill_manual(values = rev(c("black", "white"))) +
  theme_bw(base_size = 16, base_family = "Helvetica") +
  theme(aspect.ratio = 1/2) +
  theme(axis.text = element_text(color = "black")) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.5)) +
  theme(panel.grid.major = element_line(colour = "grey20")) +
  theme(panel.grid.minor = element_line(colour = "grey50")) +
  theme(panel.grid.major.x = element_blank()) +
  theme(panel.border = element_blank()) +
  theme(legend.position = "top") +
  theme(plot.margin = unit(c(0, 0, 0, 0), "lines")) +
  labs(list(
    y = "Aggressiveness",
    x = "Region"
    ))
if (!interactive()){
  ggsave(file.path("results", "figures", "publication", "aggressiveness.pdf"),
         width = 88, units = "mm")
}
```
